---
title: "Automated ML with H20 I"
date: "2023-06-12"
output: 
    html_document:
        toc: TRUE
        theme: flatly
        highlight: tango
        code_folding: hide
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE
    )
```

# Challenge Summary

Use your learning from descriptive features and plot_ggpairs() to further investigate the features. Run the functions above according to the features needed. Answer the following questions. Most of the time, you will only need the images from diagonal.

# Libraries

Load the following libraries. 


```{r}
# install.packages("plotly")

library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel) # Addon for ggplot, so that the labels do not overlap

library(readxl)
library(skimr)
library(GGally)

```

# Helper functions


```{r}
plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
  
  color_expr <- enquo(color)
  if (rlang::quo_is_null(color_expr)) {
    
    g <- data %>%
      ggpairs(lower = "blank") 
    
  } else {
    
    color_name <- quo_name(color_expr)
    g <- data %>%
      ggpairs(mapping = aes_string(color = color_name), 
              lower = "blank", legend = 1,
              diag = list(continuous = wrap("densityDiag", 
                                            alpha = density_alpha))) +
      theme(legend.position = "bottom")
  }
  
  return(g)
}
```

# Data

```{r}
employee_attrition_tbl <- read_csv("datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
employee_attrition_tbl
```

## Compensation Features

### Interaction between Monthly Income and Attrition

The Answer would be C, because we see the Spike below 5000 with Yes.
```{r}
employee_attrition_tbl %>%
    select(Attrition, MonthlyIncome) %>%
    plot_ggpairs(Attrition)
```

### Interaction between Percent Salary Hike and Attrition

The answer would be D, because the graphs for Yes and No are largely similar.
```{r}
employee_attrition_tbl %>%
    select(Attrition, PercentSalaryHike) %>%
    plot_ggpairs(Attrition)
```

### Interaction between Stock Option Level and Attrition

The Answer would be B or C, because we can see that the majority of the people with 1 or 2 Stock Options are staying, but with 3 Stock Options they are the same and 0 Stock Options the would more likely have Attrition.
```{r}
employee_attrition_tbl %>%
    select(Attrition, StockOptionLevel) %>%
    plot_ggpairs(Attrition)
```

## Survey Results

### Interaction between Environment Satisfaction and Attrition

The Answer would be C, because the Graph for Attrition Yes is similar in all levels of satisfaction.

```{r}
employee_attrition_tbl %>%
    select(Attrition, EnvironmentSatisfaction) %>%
    plot_ggpairs(Attrition)
```

### Interaction between Work Life Balance and Attrition

The answer would be B and C, because we can see the spikes of 2's and 3's for both Yes and No
```{r}
employee_attrition_tbl %>%
    select(Attrition, WorkLifeBalance) %>%
    plot_ggpairs(Attrition)
```
## Performance Data

### Interaction between Job Involvement and Attrition

The answer would be between A and B because the lower density happens at the 1's and 4's.
```{r}
employee_attrition_tbl %>%
    select(Attrition, JobInvolvement) %>%
    plot_ggpairs(Attrition)
```
## Work-Life Features

### Interaction between Over Time and Attrition

The answer would be B, because we can see that the red portion is larger than the blue portion.
```{r}
employee_attrition_tbl %>%
    select(Attrition, OverTime) %>%
    plot_ggpairs(Attrition)
```
## Training and Education

### Interaction between Training Times Last Year and Attrition

The answer is C, because both graphs for Yes and No are similar.
```{r}
employee_attrition_tbl %>%
    select(Attrition, TrainingTimesLastYear) %>%
    plot_ggpairs(Attrition)
```
## Time-Based Features

### Interaction between Years At Company and Attrition

The answer would be B, which we can the on the spike at the beginning of the graph for Years < 10.
```{r}
employee_attrition_tbl %>%
    select(Attrition, YearsAtCompany) %>%
    plot_ggpairs(Attrition)
```
### Interaction between Years Since Last Promotion and Attrition

The answer would be C, because both graphs are similar, just with Yes having a bigger spike at the beginning.
```{r}
employee_attrition_tbl %>%
    select(Attrition, YearsSinceLastPromotion) %>%
    plot_ggpairs(Attrition)
```

Congratulations! You are done with the 3rd challenge!