---
title: "Supervised ML - Regression"
date: today()
output: 
    html_document:
        toc: TRUE
        theme: flatly
        highlight: tango
        code_folding: hide
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE
    )
```

# Challenge Summary

In this session we did not use the recipes packages to prepare our data. This is going to be your challenge. For further information take a look at the last session or just use google. Prepare the data for the models with the steps provided below. Remember, you don’t need to set the flags by yourself (see all_nominal()).

# Libraries

Load the following libraries. 


```{r}
# install.packages("plotly")

library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel) # Addon for ggplot, so that the labels do not overlap

# Modeling
library(parsnip)

# Preprocessing & Sampling
library(recipes)
library(rsample)

# Modeling Error Metrics
library(yardstick)

# Plotting Decision Trees
library(rpart.plot)
```


# Data

```{r}

# Data set
bike_data_tbl <- readRDS("bike_orderlines.rds")
bike_data_tbl
```



Congratulations! You are done with the 2nd challenge!