---
title: "Automated ML with H20 II"
date: "2023-06-12"
output: 
    html_document:
        toc: TRUE
        theme: flatly
        highlight: tango
        code_folding: hide
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE
    )
```

# Challenge Summary

For the challenge, we shall be working with a Product Backorders dataset. The goal here is to predict whether or not a product will be put on backorder status, given a number of product metrics such as current inventory, transit time, demand forecasts and prior sales. It’s a classic Binary Classification problem. The dataset can be accessed from here:

# Libraries

Load the following libraries. 


```{r}
# install.packages("plotly")

library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel) # Addon for ggplot, so that the labels do not overlap
library(readxl)

# Preprocessing & Sampling
library(recipes)
library(rsample)

library(skimr)
library(GGally)

library(h2o)
```

# Helper functions


```{r}
extract_h2o_model_name_by_position <- function(h2o_leaderboard, n = 1, verbose = T) {
  
  model_name <- h2o_leaderboard %>%
    as.tibble() %>%
    slice(n) %>%
    pull(model_id)
  
  if (verbose) message(model_name)
  
  return(model_name)
  
}
```

# Data

```{r}

# Data set
product_tbl <- read_csv("product_backorders.csv")
glimpse(product_tbl)

```

## Loading and Splitting
```{r}

product_proc_tbl <- product_tbl %>%
  mutate_if(is.character, as.factor)

split_product_tbl <- initial_split(product_proc_tbl, prop = 0.8)
train_tbl <- training(split_product_tbl)
test_tbl <- testing(split_product_tbl)
```

## Specify the response and predictor variables
```{r}
# Try Ctrl+Shift+F10, if a cache error occurs
recipe_product <- 
  recipe(went_on_backorder ~ ., data = train_tbl) %>%
  step_zv(all_predictors()) %>%
  update_role(sku, new_role = "ID") %>%
  prep()

train_bake <- bake(recipe_product, new_data = train_tbl)
test_bake <- bake(recipe_product, new_data = test_tbl)
```
## run AutoML specifying the stopping criterion
```{r h2o_begin, cache.rebuild = TRUE}
h2o.init()

split_h2o <- h2o.splitFrame(as.h2o(train_bake), ratios = c(0.8), seed = 2597)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o <- as.h2o(test_bake)

y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)

```

```{r}
automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 30,
  nfolds            = 5 
)
```

## View the leaderboard and Save best Model
```{r saveLeader}
h2o_leaderboard <- automl_models_h2o@leaderboard
#h2o_leaderboard %>% 
#  extract_h2o_model_name_by_position(4) %>% 
#  h2o.getModel() %>%
#  h2o.saveModel(path = "../Models", force = TRUE)
h2o_leaderboard
```

## Predicting using Leader Model
```{r}
prediction_tbl <- 
  h2o_leaderboard %>% 
  extract_h2o_model_name_by_position(1) %>% 
  h2o.getModel() %>% 
  h2o.predict(newdata = test_h2o) %>%
  as.tibble()

test_bake <- test_bake %>%
  mutate("ID" = row_number())

prediction_tbl <- prediction_tbl %>%
  mutate("ID" = row_number()) %>%
  left_join(test_bake) %>%
  select(-ID)

prediction_tbl

h2o.shutdown(prompt = FALSE)
```

Congratulations! You are done with the 4th challenge!